Are populations like a circuit? Comparing isolation by resistance to a new coalescent-based method.

### 2019-04-21 isolation_by_coalescence.tex
igraph tweaks!

\begin{figure}
\centering
     \includegraphics[width=0.6\textwidth]{figs/5x3b_grid}
    \caption{The grid structure and parameter labels
    for the 5 $\times$ 3 grid with two barriers:
    movement rates between $\{2,3\}$ and $\{7,8\}$ are zero,
    as are those between $\{8,9\}$ and $\{13,14\}$.
    Values for the non-zero movement rates 
    were chosen by rounding independent draws of an exponential random variable with mean 1 
    up to the nearest tenth.
    } \label{fig:5x3b_grid}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.9\textwidth]{poplars/grid_populus_map}
    \caption{
        Model results for \textit{Populus} data,
        superimposed on a map of northwestern North America.
        Sampling locations of \textit{Populus} genomes are small circles,
        with outer color indicating species 
        (red-outlined, coastal samples are \textit{trichocarpa}, 
        blue-outlined, inland samples are \textit{balsamifera});
        circle fill color indicates how samples are grouped into discrete ``populations''.
        Large circles are placed at group centroids, and given group labels.
        Arrows are labeled by the posterior mean gene flow rate inferred under
        the coalescence time model (which also determines arrow width).
        For instance, the inferred gene flow rate from 4 to 2 is 3.0,
        while that from 2 to 4 is 0.7,
        suggesting that poplars in region 4
        have many more recent ancestors in region 2
        than poplars in region 2 do in region 4.
        Northwestern bias in gene flow between \textit{balsamifera} regions
        may reflect postglacial expansion to the south and east out of a refugium in Alaska.
        \label{fig:poplar_results}
    }
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.65\textwidth]{poplars/posterior_dists_g_populus}
    \includegraphics[width=0.65\textwidth]{poplars/grid_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        \textbf{(top)} Posterior medians (dark line),
        interquartile range (box), and middle 95\% (whiskers),
        for gene flow rates.
        \textbf{(bottom)} Posterior medians, along with edge labels that match the upper figure.
        \label{sfig:poplar_g}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=\textwidth]{poplars/posterior_dists_gam_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        Plot shows posterior medians (dark line),
        interquartile range (box), and middle 95\% (whiskers),
        for coalescence rates, labeled as in Figure~\ref{fig:poplar_results}.
        For instance, the coalescence rates for regions 4 and 8 (labeled ``gam4'' and ``gam8'')
        are inferred to be much smaller than most other regions, 
        perhaps indicating larger or older populations in southwestern British Columbia.
        \label{sfig:poplar_gam}
    }
\end{figure}

>>>>

\begin{figure}
\centering
     \includegraphics[width=0.6\textwidth]{figs/5x3b_grid}
    \caption{The grid structure and parameter labels
    for the 5 $\times$ 3 grid with two barriers:
    movement rates between $\{2,3\}$ and $\{7,8\}$ are zero,
    as are those between $\{8,9\}$ and $\{13,14\}$.
    Values for the non-zero movement rates 
    were chosen by rounding independent draws of an exponential random variable with mean 1 
    up to the nearest tenth.
    Thickness and color of arrows reflect movement rates:
    darker red arrows have smaller rates and darker blue arrows have larger rates.
    } \label{fig:5x3b_grid}
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.9\textwidth]{poplars/grid_populus_map}
    \caption{
        Model results for \textit{Populus} data,
        superimposed on a map of northwestern North America.
        Sampling locations of \textit{Populus} genomes are small circles,
        with outer color indicating species 
        (red-outlined, coastal samples are \textit{trichocarpa}, 
        blue-outlined, inland samples are \textit{balsamifera});
        circle fill color indicates how samples are grouped into discrete ``populations''.
        Large circles are placed at group centroids, and given group labels.
        Arrows are labeled by the posterior mean gene flow rate inferred under
        the coalescence time model (which also determines arrow width and color).
        For instance, the inferred gene flow rate from 4 to 2 is 3.0,
        while that from 2 to 4 is 0.7,
        suggesting that poplars in region 4
        have many more recent ancestors in region 2
        than poplars in region 2 do in region 4.
        Northwestern bias in gene flow between \textit{balsamifera} regions
        may reflect postglacial expansion to the south and east out of a refugium in Alaska.
        \label{fig:poplar_results}
    }
\end{figure}

@@

\begin{figure}
\centering
    \includegraphics[width=0.65\textwidth]{poplars/posterior_dists_g_populus}
    \includegraphics[width=0.65\textwidth]{poplars/grid_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        \textbf{(top)} Posterior medians (dark line),
        interquartile range (box), and min--max (whiskers),
        for gene flow rates.
        \textbf{(bottom)} Posterior medians gene flow rates, 
        both as a numerical label and color
        (as in other figures, red is lower and blue is larger),
        along with edge labels that match the upper figure.
        Nodes are also colored according to posterior median coalescence rate:
        grey is a high rate (small population)
        and orange is a low rate (large population).
        \label{sfig:poplar_g}
    }
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=\textwidth]{poplars/posterior_dists_gam_populus}
    \caption{
        Posterior distributions of parameters for \textit{Populus} data,
        using coalescence time inference with the model shown in Figure~\ref{fig:poplar_results}.
        Plot shows posterior medians (dark line),
        interquartile range (box), and min--max (whiskers),
        for coalescence rates, labeled as in Figure~\ref{fig:poplar_results}.
        For instance, the coalescence rates for regions 4 and 8 (labeled ``gam4'' and ``gam8'')
        are inferred to be much smaller than most other regions, 
        perhaps indicating larger or older populations in southwestern British Columbia.
        \label{sfig:poplar_gam}
    }
\end{figure}
